A Closed-Form Solution to the Doppler Imaging Problem

### 2019-08-26 tex/ms.tex
full draft [build paper]

% Title
\title{Analytic Doppler Imaging}

@@

\begin{abstract} 
We derive a closed form, analytic solution to the problem of Doppler imaging
of stellar surfaces in the limit of negligible differential rotation and
convective blueshift. The model for the observed spectrum is linear in 
both the unbroadened spectrum and the surface map of the star, provided the
latter is expressed as a sum of spherical harmonics. As a result, the 
posterior distributions of both the unbroadened spectrum and the stellar map
conditioned on each other have a closed form, analytic solution that is 
computationally trivial to evaluate. When neither the unbroadened spectrum
nor the stellar map is known a priori, the global optimum can usually be
found via a fast iterative approach that also yields a lower bound on the
uncertainties.
\xxx{%
\textbf{Mention the following things:}
Advantages of data-driven modeling $\cdot$ %
Interpretable priors $\cdot$ %
Works on blended lines $\cdot$ %
Uses the whole spectrum $\cdot$ %
Yields uncertainties! $\cdot$ %
Probably works on slow rotators $\cdot$ %
Differentiable! $\cdot$ %
Fast! $\cdot$ %
Use in MCMC to marginalize over inclination and stuff
}
%
\href{https://github.com/rodluger/paparazzi}{\color{linkcolor}\faGithub}
\end{abstract}

@@

A common approach to computing the Doppler-shifted spectrum is to
evaluate the spectrum at the rest frame wavelength $\lnlam_0$
and interpolate back to the grid in $\lnlam$. This is practical when
computing the spectrum at a single \emph{point} on the surface, but not
ideal when one is interested in the \emph{integral} over the visible
surface of the star $\Surf$, which is typically all we can observe:
%
\begin{align}
    \label{eq:the_problem:F}
    F(\lnlam, t, \Dargs) 
        &\equiv
        \iint\limits_{\Surf(\x)}
                I(\lnlam, \x, t, \Dargs)
        \mathrm{d}{\Surf(\x)}
        \quad ,
\end{align}
%
The difficulty in solving Equation~(\ref{eq:the_problem:F}) stems from the fact
that $I(\lnlam, \x, t, \Dargs)$ is difficult to write down in 
closed form, given
the non-linearity of the Doppler shift.
The standard approach to solving this integral is therefore
to discretize the surface of the star with a fine grid, evaluate the
Doppler-shifted spectrum in each cell, and sum over the spatial axes
to approximate the integral. Depending on the resolution of the grid,
this is either numerically inaccurate or computationally inefficient 
(and often both).

@@

Importantly, the framework developed here allows one to analytically
compute not only the ``optimal'' solution to the Doppler imaging problem,
but also its uncertainty. The problem of re-constructing surface images
of stars from spectra and/or light curves is fundamentally ill-posed because
of intrinsic degeneracies and a large null space
\citep[e.g.,][]{Luger2019} \xxx{more cites}. Coupled to uncertainties in
the observations themselves, this makes the process of searching for the
``optimal'' solution flawed at best, and meaningless at worst. Access to the
full covariance matrix of the solution is therefore essential to assessing our
confidence in the various features of the inferred surface maps.

However, as we mentioned above, the Doppler imaging problem can be solved
analytically for either the surface map or the spectrum, but not both. If
neither are known exactly \emph{a priori}, which is quite often the case,
we can still find the MAP solution quickly by guessing at an initial
spectrum $\bvec{s}$ and iterating between optimizing for $\bvec{y}$ and
optimizing for $\bvec{s}$. This bi-linear problem is not generally convex,
but given a good starting point for $\bvec{s}$ and sufficient regularization
on $\bvec{y}$, we find that it typically converges to the correct solution,
especially after refinement with a non-linear solver;
we discuss this in detail below.

@@

Given this new equation, we must change how we approach the inverse problem
(\S\ref{sec:inverse}). When solving for the spectrum given the spherical 
harmonic vector (\S\ref{sec:solve_s}), we need only make the replacements
$\bvec{f} \rightarrow \nicefrac{\bvec{f}}{\bvec{B}\, \bvec{y}}$
and 
$\boldsymbol{\Sigma}_\mathbf{f} \rightarrow \nicefrac{\boldsymbol{\Sigma}_\mathbf{f}}{(\bvec{B}\, \bvec{y})^2}$ 
in Equations~(\ref{eq:inverse:shat}) and (\ref{eq:inverse:scov}).
However, when solving for the spherical harmonic vector given the spectrum
(\ref{sec:solve_y}), the problem is no longer linear in $\bvec{y}$, as the
vector of interest appears in both the numerator and the denominator:
%
\begin{align}
    \label{eq:norm:fy}
    \bvec{f}
    &=
    \frac{
        \bvec{D}
        \,
        \bvec{S}
        \,
        \bvec{y}
    }{
        \bvec{B}
        \,
        \bvec{y}
    }
    \quad.
\end{align}
%
While we can solve for $\bvec{y}$ using a non-linear optimizer, it is
often the case that the denominator in Equation~(\ref{eq:norm:fy}) is close
to unity; i.e., the total flux from the star typically varies by only a
few percent. When this is the case, it is straightforward to linearize
this equation.
Following the notation from \S\ref{sec:solve_y}, we may therefore write
%
\begin{align}
    \bvec{f}
    &=
    \frac{
        \bvec{D} \, \bvec{s_0}
        \,
        + 
        \,
        \bvec{D}\bvec{S_1}
        \,
        \bvec{y_1}
    }{
        \bvec{B_0}
        \,
        +
        \bvec{B_1}
        \,
        \bvec{y_1}
    }
    \quad,
\end{align}
%
where $\bvec{B_0} = \bvec{1}$ is the first column of $\bvec{B}$
and $\bvec{B}_\bvec{1}$ denotes the
matrix composed from the remaining $N - 1$ columns of $\bvec{B}$.
Expanding the expression above about 
$\bvec{B_1} \bvec{y_1} = \bvec{0}$ and keeping only terms up to
first order, we have
%
\begin{align}
    \label{eq:norm:fapprox}
    \bvec{f}
    &\approx
    \left(
        \bvec{D} \, \bvec{s_0}
        \,
        + 
        \,
        \bvec{D}\bvec{S_1}
        \,
        \bvec{y_1}
    \right)
    \circ
    \left(
        \bvec{1}
        \,
        -
        \bvec{B_1}
        \,
        \bvec{y_1}
    \right)
    \nonumber \\
    &\approx
    \left(
        \bvec{D}\bvec{S_1}
        \,
        -
        \bvec{C}
    \right)
    \bvec{y_1}
    \,
    +
    \,
    \bvec{D} \, \bvec{s_0}
    \quad,
\end{align}
%
where $\circ$ denotes an elementwise product and $\bvec{C}$ is a matrix
constructed by multiplying each row of $\bvec{B_1}$ by the
corresponding element of $\bvec{D}\bvec{s_0}$.
%
This equation is now
linear in $\bvec{y}_\bvec{1}$, so we may solve the least-squares problem
as before:
%
\begin{align}
    \label{eq:norm:yhat}
    \bvec{\hat{y}_1} &= 
    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1}
    \left(
        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
        (\bvec{f} - \bvec{D}\bvec{s_0})
        +
        {\boldsymbol{\Lambda}_{\mathbf{y}_\bvec{1}}}^{-1} \boldsymbol{\mu}_{\mathbf{y}_\bvec{1}}
    \right)
    \quad,
\end{align}
%
with covariance
%
\begin{align}
    \label{eq:norm:ycov}
    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1} &= 
    \left(
        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)
        +
        {\boldsymbol{\Lambda}_{\mathbf{y}_1}}^{-1}
    \right)^{-1}
    \quad.
\end{align}
%
Note, importantly, that these equations are valid only in the limit that the
change in the total flux from the star is small. Nevertheless, even in the 
general case, we find that solving this linear problem yields a good
starting point for a non-linear optimization, which we revisit in more
detail below.

@@

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/twospec.pdf}
    \oscaption{twospec}{%
        An example of a star whose spectrum is different within the spot
        (\texttt{B}) and outside of the spot (\texttt{A}). Everywhere on 
        the surface, the spectrum is a linear combination of two
        ``eigenspectra'' ($s_1$ and $s_2$).
        As in Figure~\ref{fig:spot_y1bs}, we assume
        we do not know the map, the baseline, or either of the eigenspectra.
        The top row shows the true values for the map and the spectra, and
        the bottom row shows our inferred values.
        \label{fig:twospec}
    }
    \end{centering}
\end{figure}
%
\xxx{Figure~\ref{fig:twospec} shows...}

\section{Discussion}
\label{sec:discussion}
%
\subsection{Scaling of the computations}
\label{sec:scaling}
%
Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires 
first the rotation of the $(\lmax + 1)^2$
$\kT$ kernels (each of length $W$) to the correct stellar 
rotational phase, an operation that scales approximately
as $W \lmax^3$,
followed by $(\lmax + 1)^2$
linear convolutions of the rotated $\kT$ kernels with the 
spectral components (each of length $K$), which scales
approximately as $W K \lmax^2$. Since typically $K \gg \lmax$,
the latter computation dominates and the entire evaluation 
takes $\mathcal{O}(W K \lmax^2)$ operations. \xxx{More on this.}

\subsection{Dependence on SNR}
\label{sec:snr}
%
\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.98\linewidth]{figures/snr.pdf}
    \oscaption{snr}{%
        Recovered \spot map as a function of SNR per resolution element.
        The quality of the inferred map in the northern hemisphere improves
        with SNR, but at very high SNR the region surrounding the global
        optimum becomes so small that our optimization methods struggle to
        converge on the correct solution.
        \label{fig:snr}
    }
    \end{centering}
\end{figure}
%
\xxx{Figure~\ref{fig:snr} shows...}

\subsection{Dependence on inclination}
\label{sec:inc}
%
\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.98\linewidth]{figures/inclinations.pdf}
    \oscaption{inclinations}{%
        Recovered \spot map as a function of stellar inclination. The
        rest frame spectrum is assumed to be known exactly, but the
        baseline is not. At very low inclinations, the small
        projected velocities begin to degrade the spatial resolution of
        the inferred map, while at inclinations close to $90^\circ$ there
        is a degeneracy between the northern and southern hemispheres.
        \label{fig:inclinations}
    }
    \end{centering}
\end{figure}
%
\xxx{Figure~\ref{fig:inclinations} shows...}

\subsection{Miscellaneous}
\label{sec:misc}
\xxx{%
\begin{enumerate}
\item In a more realistic scenario, we'd know more info about the spectrum.
\item We are not addressing differential rotation and convective blueshift.
\item Telluric lines could be treated much as in Figure~\ref{fig:twospec}.
\item Instrumental profile is another Toeplitz matrix.
\end{enumerate}
}

\section{Conclusions}
\label{sec:conclusions}
\xxx{Conclusions here.}

>>>>

% Title
\title{A Closed-Form Solution to the Doppler Imaging Problem}

@@

\begin{abstract} 
We derive a closed form, analytic solution to the problem of Doppler imaging
of stellar surfaces in the limit of negligible differential rotation and
convective blueshift. The model for the observed spectrum is linear in the
coefficients of the spherical harmonic expansion of the specific intensity
distribution on the surface and, in certain limits, the posterior over surface maps
has a closed form, analytic solution that is computationally trivial to
evaluate. The model is also linear in the local (rest frame) stellar spectrum,
which may itself be spatially variable. This allows one to perform Doppler
imaging without knowledge of the local stellar spectrum and therefore works
on blended lines or regions of the spectrum where line formation mechanisms
are not well understood. Finally, the model is fast, differentiable, and allows
one to calculate uncertainties on the inferred surface map.
%
\href{https://github.com/rodluger/paparazzi}{\color{linkcolor}\faGithub}
\end{abstract}

@@

A common approach to computing the Doppler-shifted spectrum is to
evaluate the spectrum at the rest frame wavelength $\lnlam_0$
and interpolate back to the grid in $\lnlam$. This is practical when
computing the spectrum at a single \emph{point} on the surface, but not
ideal when one is interested in the \emph{integral} over the visible
surface of the star $\Surf$, which is typically all we can observe:
%
\begin{align}
    \label{eq:the_problem:F}
    F(\lnlam, t, \Dargs) 
        &\equiv
        \iint\limits_{\Surf(\x)}
                I(\lnlam, \x, t, \Dargs)
        \mathrm{d}{\Surf(\x)}
        \quad ,
\end{align}
%
The difficulty in solving Equation~(\ref{eq:the_problem:F}) stems from the fact
that $I(\lnlam, \x, t, \Dargs)$ is difficult to write down in 
closed form, given
the nonlinearity of the Doppler shift.
The standard approach to solving this integral is therefore
to discretize the surface of the star with a fine grid, evaluate the
Doppler-shifted spectrum in each cell, and sum over the spatial axes
to approximate the integral. Depending on the resolution of the grid,
this is either numerically inaccurate or computationally inefficient 
(and often both).

@@

Importantly, the framework developed here allows one to analytically
compute not only the ``optimal'' solution to the Doppler imaging problem,
but also its uncertainty. The problem of re-constructing surface images
of stars from spectra and/or light curves is fundamentally ill-posed because
of intrinsic degeneracies and a large null space
\citep[e.g.,][]{Cowan2017,Luger2019}. Coupled to uncertainties in
the observations themselves, this makes the process of searching for the
``optimal'' solution flawed at best, and meaningless at worst. Access to the
full covariance matrix of the solution is therefore essential to assessing our
confidence in the various features of the inferred surface maps.

However, as we mentioned above, the Doppler imaging problem can be solved
analytically for either the surface map or the spectrum, but not both. If
neither are known exactly \emph{a priori}, which is quite often the case,
we can still find the MAP solution quickly by guessing at an initial
spectrum $\bvec{s}$ and iterating between optimizing for $\bvec{y}$ and
optimizing for $\bvec{s}$. This bilinear problem is not generally convex,
but given a good starting point for $\bvec{s}$ and sufficient regularization
on $\bvec{y}$, we find that it typically converges to the correct solution,
especially after refinement with a nonlinear solver;
we discuss this in detail below.

@@

Given this new equation, we must change how we approach the inverse problem
(\S\ref{sec:inverse}). When solving for the spectrum given the spherical 
harmonic vector (\S\ref{sec:solve_s}), we need only make the replacements
$\bvec{f} \rightarrow \nicefrac{\bvec{f}}{\bvec{B}\, \bvec{y}}$
and 
$\boldsymbol{\Sigma}_\mathbf{f} \rightarrow \nicefrac{\boldsymbol{\Sigma}_\mathbf{f}}{(\bvec{B}\, \bvec{y})^2}$ 
in Equations~(\ref{eq:inverse:shat}) and (\ref{eq:inverse:scov}).
However, when solving for the spherical harmonic vector given the spectrum
(\ref{sec:solve_y}), the problem is no longer linear in $\bvec{y}$, as the
vector of interest appears in both the numerator and the denominator:
%
\begin{align}
    \label{eq:norm:fy}
    \bvec{f}
    &=
    \frac{
        \bvec{D}
        \,
        \bvec{S}
        \,
        \bvec{y}
    }{
        \bvec{B}
        \,
        \bvec{y}
    }
    \quad.
\end{align}
%
While we can solve for $\bvec{y}$ using a nonlinear optimizer, it is
often the case that the denominator in Equation~(\ref{eq:norm:fy}) is close
to unity; i.e., the total flux from the star typically varies by only a
few percent. When this is the case, it is straightforward to linearize
this equation.
Following the notation from \S\ref{sec:solve_y}, we may therefore write
%
\begin{align}
    \bvec{f}
    &=
    \frac{
        \bvec{D} \, \bvec{s_0}
        \,
        + 
        \,
        \bvec{D}\bvec{S_1}
        \,
        \bvec{y_1}
    }{
        \bvec{B_0}
        \,
        +
        \bvec{B_1}
        \,
        \bvec{y_1}
    }
    \quad,
\end{align}
%
where $\bvec{B_0} = \bvec{1}$ is the first column of $\bvec{B}$
and $\bvec{B}_\bvec{1}$ denotes the
matrix composed from the remaining $N - 1$ columns of $\bvec{B}$.
Expanding the expression above about 
$\bvec{B_1} \bvec{y_1} = \bvec{0}$ and keeping only terms up to
first order, we have
%
\begin{align}
    \label{eq:norm:fapprox}
    \bvec{f}
    &\approx
    \left(
        \bvec{D} \, \bvec{s_0}
        \,
        + 
        \,
        \bvec{D}\bvec{S_1}
        \,
        \bvec{y_1}
    \right)
    \circ
    \left(
        \bvec{1}
        \,
        -
        \bvec{B_1}
        \,
        \bvec{y_1}
    \right)
    \nonumber \\
    &\approx
    \left(
        \bvec{D}\bvec{S_1}
        \,
        -
        \bvec{C}
    \right)
    \bvec{y_1}
    \,
    +
    \,
    \bvec{D} \, \bvec{s_0}
    \quad,
\end{align}
%
where $\circ$ denotes an elementwise product and $\bvec{C}$ is a matrix
constructed by multiplying each row of $\bvec{B_1}$ by the
corresponding element of $\bvec{D}\bvec{s_0}$.
%
This equation is now
linear in $\bvec{y}_\bvec{1}$, so we may solve the least-squares problem
as before:
%
\begin{align}
    \label{eq:norm:yhat}
    \bvec{\hat{y}_1} &= 
    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1}
    \left(
        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
        (\bvec{f} - \bvec{D}\bvec{s_0})
        +
        {\boldsymbol{\Lambda}_{\mathbf{y}_\bvec{1}}}^{-1} \boldsymbol{\mu}_{\mathbf{y}_\bvec{1}}
    \right)
    \quad,
\end{align}
%
with covariance
%
\begin{align}
    \label{eq:norm:ycov}
    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1} &= 
    \left(
        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)
        +
        {\boldsymbol{\Lambda}_{\mathbf{y}_1}}^{-1}
    \right)^{-1}
    \quad.
\end{align}
%
Note, importantly, that these equations are valid only in the limit that the
change in the total flux from the star is small. Nevertheless, even in the 
general case, we find that solving this linear problem yields a good
starting point for a nonlinear optimization, which we revisit in more
detail below.

@@

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/twospec.pdf}
    \oscaption{twospec}{%
        An example of a star whose spectrum is different within the spot
        (\texttt{B}) and outside of the spot (\texttt{A}). Everywhere on 
        the surface, the spectrum is a linear combination of two
        spectral components ($s_1$ and $s_2$).
        As in Figure~\ref{fig:spot_y1bs}, we assume
        we do not know the map, the baseline, or either of the spectra.
        The top row shows the true values for the map and the spectra, and
        the bottom row shows our inferred values.
        \label{fig:twospec}
    }
    \end{centering}
\end{figure}
%
We set \bvec{s_1} equal to a flat spectrum with two absorption lines of
different depths, and \bvec{s_2} to the same spectrum, except we make the
second line an emission feature. The local rest-frame spectrum everywhere on the 
surface is a linear combination of these two spectra. In our simple problem,
the weight given to the first spectrum is the same everywhere (encoded in 
the first row of $\mathbb{Y}^\top$), and the weight
given to the second spectrum is large outside of the spot and small within
the spot (encoded in the second row of $\mathbb{Y}^\top$, which we set equal
to the spherical harmonic expansion of the \spot feature).
The first row of Figure ~\ref{fig:twospec} shows the problem setup. The two
spectral components are shown as the blue ($\bvec{s_1}$) and green
($\bvec{s_2}$) curves at the right. Point \texttt{A} on the map (left panel)
is outside the spot feature, so its local spectrum has nearly equal
contributions from $\bvec{s_1}$ and $\bvec{s_2}$, and the second spectral
line is absent (center panel). Point \texttt{B} is inside the spot, so
it receives a contribution from $\bvec{s_1}$ only.

In our inference step, we again assume we have no knowledge of the map,
the baseline, or either of the spectral components. As before, we initialize 
$\bvec{s_1}$ to the deconvolved mean spectrum and $\bvec{s_2}$ to the
deconvolved mean spectrum after subtracting $\bvec{s_1}$. In practice this
leads to a decent approximation to $\bvec{s_1}$ but a rather featureless
guess for $\bvec{s_2}$. We use the same priors as before, except we 
set $\sigma_\bvec{s_1} = \sigma_\bvec{s_2} = 0.01$ to force the continuum
to be flatter. We run our bilinear solver with $T_0 = 5,000$ and 
$\Delta\log T = -0.025$ followed by the nonlinear solver with
$N_\mathrm{nadam} = 2,000$ and $L_\mathrm{nadam} = 3\times 10^{-4}$.

The results are shown in the bottom panel of Figure~\ref{fig:twospec}.
We recover the \spot feature reasonably well, although with more artifacts
than in the previous experiments. We also recover the two spectral components,
although our solution for $\bvec{s_2}$ is significantly better than that for
$\bvec{s_1}$. This is due to the fact that the only information
about $\bvec{s_1}$ that makes it into our dataset is the convolution of
$\bvec{s_1}$ with the first term of the convolution kernel
$\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{figures/kT00.pdf}}),
since this spectral component has no spatial variability.
Since the deconvolution operation is in general ill-posed, there is no
unique solution for $\bvec{s_1}$. On the other hand, the other spectral
component projects into the data via convolutions with all other
terms of the kernel and is therefore very well constrained.
Finally, we can estimate the spectra at points \texttt{A} and \texttt{B}
as before (center panel). We recover the single spectral line at \texttt{A}
and the two lines at \texttt{B}, albeit rather noisily due to the uncertainty
in $\bvec{s_1}$.

\section{Discussion}
\label{sec:discussion}
%

\xxx{%
\begin{enumerate}
    %
    \item%
    A gaussian prior with unit mean is a pretty bad prior for the spectrum.
    In a more realistic scenario, we'd know a lot more information about the
    spectrum---such as where the lines are and some estimate of their shapes
    and depths---so the fidelity of our maps would be higher.
    %
    \item We are not addressing differential rotation and convective blueshift.
    These make the integral in Equation~(\ref{eq:deconv:kT}) very difficult
    to solve. We will tackle this in the next paper.
    %
    \item Telluric lines could be treated much as in Figure~\ref{fig:twospec},
    and marginalized over as in \citet{Bedell2019}.
    %
    \item The instrumental profile is another Toeplitz matrix that can be
    dotted into Equation~(\ref{eq:linear:f}).
    %
    \item Discuss the case where the inclination/period/velocity is unknown.
    The problem is not linear in these variables, so we need MCMC. But our
    model is differentiable, so we can easily use HMC. Discuss.
    %
    \item%
    Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires 
    first the rotation of the $(\lmax + 1)^2$
    $\kT$ kernels (each of length $W$) to the correct stellar 
    rotational phase, an operation that scales approximately
    as $W \lmax^3$,
    followed by $(\lmax + 1)^2$
    linear convolutions of the rotated $\kT$ kernels with the 
    spectral components (each of length $K$), which scales
    approximately as $W K \lmax^2$. Since typically $K \gg \lmax$,
    the latter computation dominates and the entire evaluation 
    takes $\mathcal{O}(W K \lmax^2)$ operations.
\end{enumerate}
}

\subsection{Dependence on SNR}
\label{sec:snr}
%
Most of the examples in this paper considered very high SNR spectra.
Figure~\ref{fig:snr} shows the effect of different SNR on the quality
of the inferred map. As before, the SNR we report is the ratio of the
standard deviation of the true model in each wavelength bin across 
all epochs, averaged over all wavelength bins (i.e., the ``signal'') to the 
standard deviation of the added noise term, $\sigma_\bvec{f}$ (the ``noise'').
The panels in Figure~\ref{fig:snr} show the inferred map for SNR in the range
1---1000, where SNR $\sim 100$ is the fiducial case considered in the
examples so far. The setup is the same as that in \S\ref{sec:spot_y1b}, where
the spectrum is known exactly but the map coefficients and the baseline are
not.

As may be expected, the quality of the map decreases with lower SNR, but
a reduction of the SNR by $\sim 20\times$ still allows for reasonable
recovery of the \spot feature. In general, as the SNR decreases further, 
two things happen: the \spot contrast decreases, and the features begin to
blur out, especially south of about $+30^\circ$ latitude, where features 
are more limb-darkened
at this inclination and in view for a smaller fraction of the time.

As the SNR incraeses, however, the quality of the \spot feature does not
improve appreciably, since a SNR of 100 is more than sufficient to recover 
a $l_\mathrm{max} = 15$ band-limited map. Interestingly, south of the equator,
the map quality actually begins to degrade with higher SNR. This is due to
the fact that finding the global optimum becomes exponentially more difficult
with higher SNR, as the posterior volume becomes ever smaller. Even with
aggressive tempering, we were unable to converge on the best solution for
SNR $\gtrsim 500$ given our standard, conservative priors and initial
guesses (\S\ref{sec:spotstar}).
%
\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.98\linewidth]{figures/snr.pdf}
    \oscaption{snr}{%
        Recovered \spot map as a function of SNR per resolution element.
        The quality of the inferred map in the northern hemisphere improves
        with SNR, but at very high SNR the region surrounding the global
        optimum becomes so small that our optimization methods struggle to
        converge on the correct solution.
        \label{fig:snr}
    }
    \end{centering}
\end{figure}
%
\subsection{Dependence on inclination}
\label{sec:inc}
%
\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.98\linewidth]{figures/inclinations.pdf}
    \oscaption{inclinations}{%
        Recovered \spot map as a function of stellar inclination. The
        rest frame spectrum is assumed to be known exactly, but the
        baseline is not. At very low inclinations, the small
        projected velocities begin to degrade the spatial resolution of
        the inferred map, while at inclinations close to $90^\circ$ there
        is a degeneracy between the northern and southern hemispheres.
        \label{fig:inclinations}
    }
    \end{centering}
\end{figure}
As in \citet{Vogt1987},
we also investigate the dependence of the solution on the inclination
of the star.
Figure~\ref{fig:inclinations} shows the inferred map for the same problem
setup as before (with SNR $\sim 100$), but this time varying the
inclination between $10^\circ$ (nearly face-on) and $90^\circ$ (perfectly
edge-on). As before, the inclination is assumed to be known exactly. We
further keep the true equatorial velocity of the star constant across
all panels, so that the figure corresponds to the same star viewed at
different orientations. Because of this, decreasing the inclination
decreases $v\sin i$, reducing the width of the convolution kernel and
therefore the spatial resolution of our inferred map. Increasing the
inclination does not result in appreciable changes until an inclination of
$\sim 80^\circ$, above which it becomes difficult to differentiate between
features in the northern and southern hemispheres, whose projected
velocities are nearly equal. At $i = 90^\circ$, there is a formal
degeneracy between the two hemispheres, which can be seen from the
mirror-image symmetry in the inferred map. These results are broadly consistent
with those of \citet{Vogt1987}.

\section{Conclusions}
\label{sec:conclusions}
\xxx{%
\begin{enumerate}
    \item Advantages of data-driven modeling
    \item Interpretable priors
    \item Works on blended lines
    \item Uses the whole spectrum
    \item Yields uncertainties!
    \item Probably works on slow rotators
    \item Differentiable!
    \item Fast!
    \item Use in MCMC to marginalize over inclination and stuff
\end{enumerate}
}
